\documentclass[a4paper,10pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{#2} \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[2]{\resumeItem{\textbf{#1}{: #2}}}
\renewcommand{\labelitemii}{$\circ$}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\begin{center}
    \textbf{\Huge Bhavya Mishra} \\[1pt]
    Bhopal, India \\
    \href{mailto:mishra24bhavya@gmail.com}{mishra24bhavya@gmail.com} ~|~ +91 8447067123
\end{center}

%-----------EDUCATION-----------
\section*{Education}
\resumeSubheading
  {B.Tech in Bioengineering}{2022 -- 2026}
  {Vit Bhopal University}{Bhopal, India}

\resumeSubheading
  {Higher Secondary Schooling}{Completed 2022}
  {Sant Gyaneshwar Model School (CBSE)}{Lakshmi Enclave, Delhi}

\resumeSubheading
  {Secondary Schooling}{Completed 2020}
  {Apeejay School Noida (CBSE)}{Noida, India}

\resumeSubheading
  {Bachelor of Arts in Bharatnatyam}{Completed 2021}
  {Thyagraja Centre for Music and Dance (Affiliated to Prayag Sangeet Samiti)}{Prayagraj, India}

%-----------PROJECTS & RESEARCH-----------
\section*{Projects \& Research Work}
\resumeItem{\textbf{Literature Review: Rare Diseases} (Aug 2024)
\begin{itemize}
  \item Conducted a systematic literature review on Hutchinson-Gilford Progeria Syndrome, ALS, and Harlequin Ichthyosis.
  \item Focused segment on Progeria using PubMed and Google Scholar.
\end{itemize}}

\resumeItem{\textbf{Bioinformatics Modules and Lab Work} (Mar 2025)
\begin{itemize}
  \item Explored evolutionary relations, phylogenetic trees, sequential alignment, FASTA and BLAST.
  \item Utilized CLUSTAL-W, UniProt, GenBank, EMBL, NCBI, DDBJ, GenScan.
\end{itemize}}

\resumeItem{\textbf{Comprehensive Study of Bullet Trains in India} (Sep 2023)
\begin{itemize}
  \item Analyzed biomimicry design of Shinkansen trains, their evolution and Indian adaptation.
  \item Integrated research via Google Scholar; part of Engineering and Design Modeling course.
\end{itemize}}

\resumeItem{\textbf{Influence of Dehydration on Bioimpedance Signals} (Oct 2024)
\begin{itemize}
  \item Investigated effect of dehydration on impedance using Kaggle dataset and Orange ML tool.
  \item Developed linear regression model using 5 individuals’ hydration data; hypothesis validated.
  \item Submitted in research paper format.
\end{itemize}}

\resumeItem{\textbf{Effectiveness of Cohort Studies in Public Health} (Aug 2024)
\begin{itemize}
  \item Authored a short article highlighting use and limitations of cohort studies in India.
  \item Developed through insights gained in Global Health Challenges course.
\end{itemize}}

\resumeItem{\textbf{Improving Healthcare Systems} (May 2025)
\begin{itemize}
  \item Created scientific article analyzing Indian healthcare structure and improvement pathways.
  \item Based on Coursera course by Johns Hopkins University.
\end{itemize}}

\resumeItem{\textbf{Cancer Biology} (June 2025)
\begin{itemize}
  \item Designed a cancer research project integrating class notes and studies from PubMed.
  \item Completed after three-part Coursera course on cancer biology.
\end{itemize}}

\resumeItem{\textbf{Inherited Futures} (June 2025)
\begin{itemize}
  \item Wrote a literature review on ethical dilemmas in clinical trials of Huntington’s and Sickle Cell Anemia.
  \item Based on Alison course on Principles of Bioethics; used PubMed, Google Scholar, ResearchGate.
\end{itemize}}

%-----------CERTIFICATIONS-----------
\section*{Certifications \& Online Courses}
\resumeItem{Biomaterials: Introduction to Biomedical Engineering – Udemy}
\resumeItem{DNA Replication and its Types – Mind Luster}
\resumeItem{Animal Biotechnology Fundamentals – Mind Luster}
\resumeItem{Bioinformatics Databases – Mind Luster}
\resumeItem{Public Speaking Assessment – Learntube}
\resumeItem{Python Essentials – Vityarthi}
\resumeItem{Fundamentals of AI/ML – Vityarthi}
\resumeItem{MATLAB Course – College-provided}

%-----------ACHIEVEMENTS-----------
\section*{Achievements}
\resumeItem{Managed Annual Fest hosted by college}
\resumeItem{Represented state in a cultural event for Goa Governor}
\resumeItem{1\textsuperscript{st} Prize in Classical Dance – Thyagraja Institute}
\resumeItem{1\textsuperscript{st} Prize in Folk Dance – Thyagraja Institute}
\resumeItem{Silver Medalist in Yoga – Inter-school Competition}
\resumeItem{Core Member of Dance Club – VIT Bhopal University}

\end{document}

